% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Ravindra Mehrotra}

\basicInfo{
  \email{raviindra@hotmail.com} \textperiodcentered\ 
  \phone{(+1) 443-255-5631} \textperiodcentered\ 
  \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}}
  
Senior Database Management professional 20+ of successful experience with proven track record of RDBMS implementation, data Integration, data conversion, database Administration, database design, database replication and project management. Led and managed large scale, complex enterprise database solutions for Federal, State and private Corporations. A highly accomplished professional with ability to motivate work forces to build customized software development organizations focused on teamwork and results. Excel in leading teams in fast paced and rapid changing environment.

\section{\faBlackTie\ Areas of Expertise}
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
  \item	Installing and Managing Oracle Database 5.x/6.x/7.x/8.x/9.x/10g.x/11g.x/12c.x. 
  \item	OEM 10.x/11.x/12c.x
  \item	Database Development PL/SQL, TSQL 
  \item	Data Conversion, ETL using PL/SQL, SSMS, Oracle Goldengate
  \item	Oracle utilities Export /Import Data Pump, debug , tracing event, ADDM,ASH, TFA
  \item	Database Patching Management
  \item	Managing priority tickets on Oracle Support for  SR’s
  \item	On-Call round the clock database support for 800+ databases or 500+ servers.
  \item	Real Application Clusters (RAC), ASM, Active DataGuard,  RMAN Backups 
  \item	Database cloning, database duplication using RMAN.
  \item	Application Knowledge of Healthcare, Administration Highway, Telecommunications
  \item	Worked extensively on database design on EHR , QRDA, Registry, QCDR and Claims
  \item	Oracle Golden Gate, Advance Replication, Advance Queue Management
  \item	SQL Server 7.0 /12/16  SSIS, SSMS
  \item	Knowledge of PostgreSQL database administration and Oracle migration. 
  \item	Knowledge of Python scripting
  \item	VMWARE 5.x,6.x, Virtual Box, SAN, RAID Disks, ERWIN 6.x/7.x/8.x
  \item	Ticket Management with SNOW, Remedy, HP ALM 
  \item	UNIX, Oracle Linux, Window Server 2000/2003/2008/2012.
  \item	Java, C, Pascal, COBOL, Clipper, Pro-C, Pro-Cobol, JCL, CICS.
  \item	PMP certified Project Manager for Database projects.
  \item	Managed database Project on RDBMS Migration, Conversion patch Management, Database configuration, Design, Development, Integration, Backup, Recovery, Replication, Deployment and production support.
  \item	Waterfall SDLC and Agile Framework.
  \item	Requirement Management.
  \item	Risk Analysis and Gap analysis in database design, ETL process, data mitigation and correction.

\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2013 -- Present}
\textit{Master student} in Electronics Engineering (EE), expected March 2016
\datedsubsection{\textbf{Xidian University}, Shaanxi, China}{2009 -- 2013}
\textit{B.S.} in Electronics Engineering (EE)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
\role{Summer Intern}{Manager: xxx}
Brief introduction: xxx.
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
Brief introduction: xxx
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
\role{\LaTeX, Maintainer}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
